S2 pioneer factor MS

### 2022-11-18 manuscript/manuscript.Rmd
update methods section
add results outline to MS

## Ectopic pioneer factors bind and open closed chromatin

@@

## Twist binds closed chromatin extensively and opens chromatin at some sites

## Motif content distinguishes chromatin opening by Twist from Zelda and Grainy head

## Ectopic transcription factors bind nonspecifically to active chromatin

>>>>

## Ectopically expressed pioneer factors bind and open closed chromatin

-   Gain of function system is necessary to understand mechanisms of PF activity

-   Establish system for ectopic expression of pioneer factors

-   Identification of physiological expression levels

-   Define binding classes I-III and describe characteristics (distribution, promoters/enhancers, etc.)

@@

-   Description of RNA-seq data: number of differential genes, overlap with ChIP data, GO analysis.

-   Comparison of RNA-seq and ATAC data: chromatin opening correlates with transcriptional activation.

-   Class III promoters are most likely to be associated with upregulated genes

## Twist binds closed chromatin extensively and opens chromatin at a subset of sites

-   Introduce Twist and justify the comparison to Zld/Grh.

-   Twi binds closed chromatin and opens at some sites

-   Class I-III sites, distribution, etc.

-   Twi also promotes transcriptional activation.

-   Description of RNA-seq data: number of differential genes, overlap with ChIP data, GO analysis.

-   Comparison of RNA-seq and ATAC

## Ectopically expressed transcription factors bind opportunistically to active chromatin

-   Overlap of class I regions suggests nonspecific binding

-   Analysis of published ChIP data shows that class I regions are within active chromatin

-   RNA-seq and ATAC-seq for class I to show that the binding is not functional

## Class II and III regions are mostly in naïve chromatin

-   Analysis of chromatin at class II-III regions: mostly devoid of histone modifications

-   Class III regions have higher H3 and H1 occupancy compared to class II

-   Class II and III have poorly positioned nucleosomes

## Chromatin opening by pioneer factors is driven by motif content

-   De novo motif enrichment for ChIP peaks (supplemental)

-   Motif analysis

## Ectopic Zld, Grh and Twi fail to access many endogenous binding sites

## Repressive chromatin is a barrier to pioneer-factor binding

## Pioneer-factor binding and chromatin opening is concentration dependent

## Regions outside the DNA-binding domain are required for binding and opening of closed chromatin
